Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey

### 2017-08-22 cloverflow_technical_report/cloverflow_survey_rn.tex
Continued working on the technical report.

\subsection{Answerer Survey}
We received 113 answers (38\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{survey_exp_1-crop}
		\caption{Group 1}
		\label{fig:survey_group1_exp}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{survey_exp_2-crop}
		\caption{Group 2}
		\label{fig:survey_group2_exp}
	\end{subfigure}
	\caption{Experience of the Stack Overflow answerers}
	\label{fig:survey_exp}
\end{figure}

The majority of users in both groups are experienced developers 
with more than 10 years of experience or between 5 to 10 years 
as depicted in Figure~\ref{fig:survey_exp}. They are active users and
regularly answer questions on Stack Overflow.
Eighty one and sixty percent of users from Group 1 and Group 2 
answer questions at least once a week.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently do or did you answer questions on Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently do or did you include code snippets in your answers on Stack Overflow?}
	}%
}
\vspace{0.5cm}

\subsection{RQ1: Where are the code snippets in Stack Overflow answers from?}

To answer this research question, we ask the participants this question:

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Where did the code snippets in your answers come from?}
	}%
}
\vspace{0.5cm}

From the answers, a large amount of 91 (81\%) and 58
(68\%) answerers in both group include code snippets in more than sixty percent of
their answers. Figure~\ref{fig:survey_snippet_source} explains where are these code
snippets from. Stack Overflow answerers mostly write new code from scratch 
or modify from the code snippets in question for each answer, while 
fewer numbers are from other sources including their personal projects, 
their company projects, open source projects. We found 27 answerers in both Group 1
and Group 2 occasionally to very frequently copy code from open source projects.

@@

\begin{figure}
	\begin{subfigure}{5\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_1}
		\caption{Group 1}
		\label{fig:survey_license_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_2}
		\caption{Group 2}
		\label{fig:survey_license_2}
	\end{subfigure}
	\caption{Software license in Stack Overflow code snippets.}
	\label{fig:survey_license}
\end{figure}

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{Outdated code occurs when code snippets in your answers are no longer up-to-date with the latest version of the software you copied the code from. Have you ever been notified of outdated code in your Stack Overflow answers?}
	}%
}
\vspace{0.5cm}

We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 47.6\% in
Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
are aware of their outdated code in some of their answers.

\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{survey_outdated}
	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
	\label{fig:survey_outdated}
\end{figure}%

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently were you notified of outdated or deprecated code in your Stack
			Overflow answers?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you fix your outdated code on Stack Overflow?}
	}%
}
\vspace{0.5cm}

We then asked the participants to have been notified of their outdated code
(80 and 48 participants from Group 1 and 2 respectively) a
follow-up questions ``how frequently did you fix your outdated code on Stack
Overflow?''. The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that
more than half of them frequently fix the outdated code snippets. However, there
are 18.8\% of the answerers in both groups who rarely or never fix their code.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{survey_outdated_fix_1}
		\caption{Group 1}
		\label{fig:survey_outdated_fix_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{survey_outdated_fix_2}
		\caption{Group 2}
		\label{fig:survey_outdated_fix_2}
	\end{subfigure}
	\caption{Frequency of the answerers fixing their outdated code.}
	\label{fig:survey_outdated_fix}
\end{figure}

\subsection{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
	}%
}
\vspace{0.5cm}

More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
of them do not include license statement in their code snippets (as depicted in
Figure~\ref{fig:survey_license}) due to several reasons. First, some answerers chose to 
post only their own code or code that was adapted from the question, hence
they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
company or open source projects that they knew were permitted to be publicly distributed.
Third, some answerers believe that code snippets in their answers are too small 
to claim any intellectual property on them and fall under fair use~\citep{fairuse}.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Do you usually include a software license in your code snippets on Stack Overflow?}
	}%
}
\vspace{0.5cm}

@@

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.85\linewidth]{survey_license_check_1}
		\caption{Group 1}
		\label{fig:survey_license_check_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.85\linewidth]{survey_license_check_2}
		\caption{Group 2}
		\label{fig:survey_license_check_2}
	\end{subfigure}
	\caption{Frequency of the answerers checking license of their code snippets against Stack Overflow's CC BY-SA 3.0.}
	\label{fig:survey_license_check}
\end{figure}

@@

>>>>

\subsection{Answerer Responses}
We received 113 answers (38\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

\subsubsection*{General Information}
%General information of the answerers' experience and frequency of answering 
%questions on Stack Overflow with code snippets as discussed below.

%\subsubsection*{Q1: How long have you been working on developing software?}

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{survey_exp_1}
		\caption{Group 1}
		\label{fig:survey_group1_exp}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{survey_exp_2}
		\caption{Group 2}
		\label{fig:survey_group2_exp}
	\end{subfigure}
	\caption{Experience of the Stack Overflow answerers}
	\label{fig:survey_exp}
\end{figure}

The majority of users in both groups are experienced developers 
with more than 10 years of experience or between 5 to 10 years 
as depicted in Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that have more than 10 year of software development experience, while a slightly less percentage of 50\% in Group 2.

The participants are active users and regularly answer questions on Stack Overflow (see Figure~\ref{fig:survey_answer_frequency}). Ninety two (81\%) and fifty one (61\%) of answerers from Group 1 and Group 2  answer questions at least once a week.

More than half of the answerers very frequently (81--100\% of the time) or frequently (61--80\% of the time) include code snippets in their answers. To break down into two groups as depicted in Figure~\ref{fig:survey_answer_frequency_with_code},
Group 1 very frequently (48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise, Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).

%\subsubsection*{How frequently do or did you answer questions on Stack Overflow?}

\begin{figure}
		\centering
		\includegraphics[width=0.8\linewidth]{survey_answer_frequency}
		\caption{Frequency of answering questions}
		\label{fig:survey_answer_frequency}
\end{figure}

%\subsubsection*{How frequently do or did you include code snippets in your answers on Stack Overflow?}

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_answer_frequency_with_code_1}
		\caption{Group 1}
		\label{fig:survey_answer_frequency_with_code_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{survey_answer_frequency_with_code_2}
		\caption{Group 2}
		\label{fig:survey_answer_frequency_with_code_2}
	\end{subfigure}
	\caption{Frequency of answering questions with code snippet(s)}
	\label{fig:survey_answer_frequency_with_code}
\end{figure}

\subsubsection*{RQ1: Where are the code snippets in Stack Overflow answers from?}

To answer this research question, we ask the participants of the original
sources for their code examples. We provided six options (allowing more than one answer)
including \textit{I copied them from my own personal projects}, \textit{I copied
	them from my company's projects}, \textit{I copied them from open source
	projects}, \textit{I wrote the new code from scratch}, \textit{I copied the code
	from the question and modify it for the answer}, and \textit{Others}. From the
answers (Figure~\ref{fig:survey_snippet_source}), Stack Overflow answerers
in Group 1 mainly write new code from scratch (112) or copy from the code snippets in question
and modify it for the answer (108), followed by from their personal
projects (101), open source projects (73), other sources (57), and company projects (46). 
For Group 2, the most selected option is also writing code from scratch (83), followed by copying
from personal projects and modifying from the question (77), copying from open source projects (56),
copying from other sources (40), and copying from company projects (31).

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For research question 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time. Other less popular choices include copying code from their personal projects, and open source projects. Company projects are the least popular choice.}
	}%
}
\vspace{0.5cm}

@@

Roughly half of the top answerers on Stack Overflow
are aware of outdated code in their answers. We found that 72.3\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in at least one of their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 57.1\% in
Group 2.

\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{survey_outdated}
	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
	\label{fig:survey_outdated}
\end{figure}

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_outdated_fix_1}
		\caption{Group 1}
		\label{fig:survey_outdated_fix_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_outdated_fix_2}
		\caption{Group 2}
		\label{fig:survey_outdated_fix_2}
	\end{subfigure}
	\caption{Frequency of the answerers fixing their outdated code.}
	\label{fig:survey_outdated_fix}
\end{figure}

We then asked the participants who have been notified of their outdated code
(81 and 48 participants from Group 1 and 2 respectively) a
follow-up questions \textit{``how frequently did you fix your outdated code on Stack
Overflow?''} The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that
more than half of them frequently fix the outdated code snippets. However, there
are 19.8\% and 18.8\% of the answerers in Groups 1 and 2 who rarely or never fix their code.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.2cm]{0.98\textwidth}{%
		\textit{For research question 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them. Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
	}%
}
\vspace{0.5cm}

\subsubsection*{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}

As shown in Figure~\ref{fig:survey_license_known}, more than half of the
answerers in both groups (63.4\% and 61.9\% respectively) are aware that Stack
Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA
3.0) to content in the posts, including code snippets, while the rest of 36.6\%
and 38.1\% are not.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{survey_license_known_1}
		\caption{Group 1}
		\label{fig:survey_license_known_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{survey_license_known_2}
		\caption{Group 2}
		\label{fig:survey_license_known_2}
	\end{subfigure}
	\caption{Awareness of answerers to Stack Overflow CC BY-SA 3.0 license}
	\label{fig:survey_license_known}
\end{figure}

In addition, we found that almost all of the answerers in both groups (98\% and
99\% respectively) do not include license statement in their code snippets
(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
gave more information regarding this question in the open comment question and
we summarised them into three groups as follows. First, some answerers chose to post only their
own code or code that was adapted from the question. They are hence
automatically subjected to CC BY-SA 3.0. Second, they copied code from company
or open source projects that they knew were permitted to be publicly
distributed. Third, some answerers believe that code snippets in their answers
are too small to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{survey_license_1}
		\caption{Group 1}
		\label{fig:survey_license_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{survey_license_2}
		\caption{Group 2}
		\label{fig:survey_license_2}
	\end{subfigure}
	\caption{Software license in Stack Overflow code snippets.}
	\label{fig:survey_license}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\linewidth]{survey_license_check_1}
		\caption{Group 1}
		\label{fig:survey_license_check_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\linewidth]{survey_license_check_2}
		\caption{Group 2}
		\label{fig:survey_license_check_2}
	\end{subfigure}
	\caption{Frequency of the answerers checking license of their code snippets against Stack Overflow's CC BY-SA 3.0.}
	\label{fig:survey_license_check}
\end{figure}

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{When you had a problem with your programming tasks, please rank in which order did you search for help (1 for the first, and 5 for the last, without a tie)?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently do or did you copy source code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Why did you copy and reuse code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Have you ever found any problems from reusing Stack Overflow code snippets?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you find problems from reusing Stack Overflow code snippets?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{What were the problems?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you report the problems back to the Stack Overflow discussion threads?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How did you report the problems?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How often did you give attribution (adding a link to a Stack Overflow question/answer) as required by CC BY-SA 3.0 in the code where you used the snippet?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Have you ever checked if the Stack Overflow code snippet originated from a different source (e.g. an open source project) with an incompatible license to your project?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How often did you check for licensing conflicts of code snippets from Stack Overflow and your project(s) before using them?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you have legal problems by copying code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Could you please briefly explain what are the legal problems that you faced by copying code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Did you have any other problems from using code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}
